Spin canonical rings of log stacky curves

### 2015-07-07 curves-write-up/spin_cring.tex
remove done todo
1 change to example 3.2

We will deduce the structure of the log spin canonical ring $R_L$
from the structure of the spin canonical ring $R_{L_X} := R(X, 3
\cdot \infty, L_X)$. This technique will later be generalized
and encapsulated in the statement and proof of Lemma ~\ref{lem:sat-1}.

@@

\begin{rem}
\label{rem:base-0-377}
Examples ~\ref{eg:base-0-377}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} are used as inductive base cases in the genus 0, genus 1, and genus 1 sections respectively (see Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
\end{rem}
\todo{Some examples to add: possibly move one of the later examples up, possibly discuss adding one stacky point to a log divisor on $\BP^1$ without}

>>>>

We will deduce the structure of the log spin canonical ring $R_L$
from the structure of the spin canonical ring $R_{L_X} := R(X, 3
\cdot \infty, L_X)$. This technique will later be generalized in Lemma ~\ref{lem:sat-1}.

@@

\begin{rem}
\label{rem:base-0-377}
Examples ~\ref{eg:base-0-377}, \ref{eg:base-1-33}, and \ref{eg:exception-1-5} are used as inductive base cases in the genus 0, genus 1, and genus 1 sections respectively (see Tables ~\ref{table:g-0-base-cases} and ~\ref{table:g-1-base}).
\end{rem}
